### 2017-04-04 paper/evaluation.tex
complemented rq3

Initially, we configured Maven to output all configuration variables.
The rationale is that, for each project's module, we can capture
relevant configurations and classify their parallelization level (see
Section \ref{sec:modes}) based on their values. To avoid waiting all
tests to terminate, we just run the bootstrap phase and we skip the
actual test execution.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.}

From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with parallel execution enabled by default.
Figure~\ref{fig:freqmodes-dynamic} summarizes our findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
    caption}Distribution of parallel modes identified dynamically in a
    subset of \numProjectsPar{} projects.  A project may have support
    to more than one parallel mode. Also, a project may run only a
    subset tests in parallel by default.}
\end{figure}

>>>>

We configured Maven to output all configuration variables.  The
rationale is that, for each project's module, we can capture relevant
configurations and classify their parallelization level (see Section
\ref{sec:modes}) based on their values. To avoid waiting all tests to
terminate, we just run the bootstrap phase and we skip the actual test
execution.  According to Maven's
documentation~\cite{maven-surefire-plugin}, any parallelization
setting depends either on (1) \CodeIn{parallel} to define the
parallelism mode within a JVM followed by \CodeIn{threadCount} or (2)
\CodeIn{forkCount} (or \CodeIn{forkMode} in older versions) to define
the number of forked JVMs. For each test execution, we look for theses
parameters and their values to map to one of the possible
parallelization modes.  For instance, if a given project contains a
module with the setting \CodeIn{<forkCount>1C</forkCount>}, the
possible classifications are \ForkSeq{} or \ForkParMeth{} depending on
the presence and the value of the parameter \CodeIn{parallel}.
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our final results. Finally, some projects use a value
informed as an argument instead of adding the value statically in the
configuration value. In this case, we consider all possible values for
the parameterized parameter.  From the \numMedLong{} projects, we
identified \numProjectsPar{} projects with parallel execution enabled
by default.  Figure~\ref{tab:freqmodes-dynamic} summarizes our
findings.

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}llll}
        \toprule
        Group & Subject & - & -\\%
        \midrule%
        long   & JenkinsCI gerrit-trigger-plugin & 1 & \ForkSeq{}\\%
        medium & Jcabi & 1 & \ParClassParMeth{}\\%
        medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        medium & Apache logging-log4J2 & 25 & \ForkSeq{}\\%
        medium & Javaslang & 3 & \ParClassParMeth{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{\Fix{TODO}}
    \label{tab:freqmodes-dynamic}
\end{figure}
